\thetitle

### 2008-06-13 paper.tex
Lots of work on Common Assumptions section.

\newfootnote{\onesnote}{%
Through out this paper, $\ones{}$ denotes a matrix of all ones; dimensions of the matrix are inferred by context.
Where necessary, we disambiguate the dimensions by explicitly specifying the dimensions of the final matrix product, as we do here.
}

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The flows vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\trans{\ones{}} = \mat{V}\trans{\ones{}} \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones{}$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones{}}}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\trans{\ones{}}} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones{}}.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vector coordinates, as it does in Matlab.

@@

The total number of source flows for each node is given by the vector $\trans{\mat{S}}\ones{f} \in \R^n$, and the total number of destination flows is given by $\trans{\mat{D}}\ones{f} \in \R^n$.
The number of flows between each pair of nodes in the network is expressed by the matrix product $\trans{\mat{S}}\mat{D}\in\R^{n \times n}$.
That is $(\trans{\mat{S}}\mat{D})_{ij}$ is the number of flows from node $i$ to node $j$.
Interpreting this sparse matrix as a weighted graph immediately yields the source-destination flow communication graph.
\Figure{trace-vs-uniform} gives two visual examples of such graphs.
Similar graphs counting other quantities can readily be computed by inserting the appropriate weighting matrix.
For example, we may compute the inter-node packet transmission graph:
\begin{align}
\trans{\mat{S}}\diag(\vec{\Sigma}_\pkts)\mat{D}\in\R^{n \times n}.
\end{align}
Here $\vec{\Sigma}_\pkts$ is the byte vector defined in \Equation{packet-count}, and the ``$\diag$'' operator gives the square, diagonal matrix with the given vector of values on its diagonal.
Similar graphs for total bytes and total duration of flows may be computed using $\mat{\Sigma}_\bytes$ or $\mat{\Sigma}_\ival$ in place of $\mat{\Sigma}_\pkts$.

@@

Since uniform behaviors entail homogeneity of properties with respect to each flow individually, a trace matrix can be transformed to a matrix satisfying the model's assumptions via right matrix multiplication. Right multiplication mixes the elements within each row, and if the mixing weights are uniform, the result is uniform behavior. For example, to make the roles of the nodes with respect to each flow statistically identical, we transform $\mat{S}$ and $\mat{D}$:
\begin{align}
\mat{S}' &= \mat{S}\ones{n \times n}/n, & \mat{D}' &= \mat{D}\ones{n \times n}/n.
\end{align}
This makes all the values in each flow's row identically the average of the original $n$ values. As another example, the constant bit-rate (\caps{CBR}) flow model, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals; thus each flow's bit-rate is constant, as the name implies. The strict \caps{CBR} model can be easily expressed with the packets-bytes-duration (\caps{PBD}) model used as an example in \Section{representations}. The pair of matrices $[\mat{Z}~\mat{V}]$ is transformed to \caps{PBD} form using the vectors defined in \Section{flow-totals}: $[\mat{Z}~\mat{V}]\,\mat{\Gamma}\in\R^{f \times 3}$, where
\begin{align}
\mat{\Gamma}=\begin{pmatrix}
\ones{} & \vec{\sigma} & \zeros{} \\
\zeros{} & \zeros{} & \vec{\tau}
\end{pmatrix} \in \R^{(d_v+d_z)\times{3}}.
\end{align}
\Figure{trace-vs-uniform} graphically depicts examples of uniform behaviors as compared to realistic behaviors from traces.
%By replacing $\mat{S}'$ with $\mat{S}$, this can also be viewed as a set of linear constraints on the matrix $\mat{S}$, providing a proscriptive definition

%We use the term \textit{uniformity} do describe assumptions made about the ``sameness'' of various properties of flows. The constant bit-rate (\caps{CBR}) model, for example, is an assumption about the uniformity of all of a flow's packets: i.e. that they have the same size and are evenly spaced in time. While this is the strictest sense of the \caps{CBR} model, it is rare for this assumption to be made in isolation. Another common simplification is to make the sizes of flows identical, or chose them randomly from a uniform distribution; similarly for the starting time of each flow. Finally, when choosing endpoints for a given flow, lacking a better model, it is not unusual to treat all nodes identically, making each an equally likely source or destination for a given flow.

%It is common in generating traffic behaviors for experiments to treat packets, nodes, and flows uniformly to varying degrees. This is largely because of the high complexity of doing otherwise and the lack of compelling alternatives. Here we examine how various notions of uniformity are expressed in the matrix model. In general, \textit{intra-flow uniformity} is effected by right multiplication, which mixes the elements in each row, whereas \textit{inter-flow uniformity} is effected by left multiplication, which mixes elements across rows. The constant bit-rate (\caps{CBR}) flow model, for example, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals; thus each flow's bit-rate is constant, as the name implies. The strict \caps{CBR} model can be easily expressed with the packets-bytes-duration (\caps{PBD}) model used as an example in \Section{representations}. The pair of matrices $\tuple{\mat{Z},\mat{V}}$ is transformed to \caps{PBD} form using the vectors defined in \Section{flow-totals}: $\tuple{\mat{Z},\mat{V}}\Gamma\in\R^{f \times 3}$, where
%\begin{align}
%\Gamma=\begin{pmatrix}
%\ones{} & \vec{\sigma} & \zeros{} \\
%\zeros{} & \zeros{} & \vec{\tau}
%\end{pmatrix} \in \R^{(d_v+d_z)\times{3}}.
%\end{align}

@@

Marginality is an orthogonal concept to uniformity: the distribution of some property is identical \textit{across} all flows. For example, if we determine a distribution of flow sizes across the entire network and assume that this distribution applies \textit{independent of other flow properties}, this is a marginal model for flow size. Marginal behavior is effected by left multiplication by a matrix with uniform columns. This specific example is generated by left-uniformizing the flow size matrix: $\mat{B}' = (\ones{f \times f}/f)\mat{B}$.
The traffic models proposed by {\FHC} are all marginal: they propose certain network-wide parametric distributions for start times, flow sizes and the number of flows per node. These models do not account for non-independence between these and other flow properties. We will discuss this limitation and its implications when we analyze our experimental results.

@@

The final form of homogenization we consider, is conditionality. This is a restricted form of marginality: we may assume that marginal distributions apply to all the flows in certain groupings. For example, we can provide a distribution of flow sizes on a per-source basis. That is, each source node can have its \textit{own} distribution, and the sizes of its flows are drawn from that distribution, independent of their other properties. This is simply accomplished by left-multiplication by a non-uniform matrix. For example, to make flow behavior uniform on a per source basis, we left-multiply by the ``source-conditioning'' matrix: $\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$. Per destination uniformity can be achieved similarly, with left-multiplication by a corresponding destination-conditioning matrix: $F'=(\trans{\mat{DD}}/f)\mat{F}$.
%Although assumptions about uniformity across flows are common, there is little agreement about which notion of uniformity is most appropriate; often it is simply left unspecified. The confusion arises due to the lack of a unique way of associating flows with nodes. Each node can equally viably be associated with its source or its destination. Which association is more valid? Consider a web request: should the behavior of the request be determined by what the client typically does? Or should the requests that the server typically receives determine behavior? There is no armchair answer: only analysis of real data can give us the answer. The matrix model provides an analytical framework for doing so.
The matrix model has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the aggregate behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = \frac{1}{f}((1-\alpha)(\trans{\mat{SS}})+\alpha(\trans{\mat{DD}}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.

%We use the terms here to distinguish three fundamentally different types of assumptions about behavioral homogeneity.

%Existing traffic models are typically not explicit methods of generating complete synthetic traces of network traffic, but rather descriptions of some aspect of of the behavior of idealized traffic. In our algebraic modeling framework, such models can be interpreted as stipulations about the form of the behavior matrices, or as transforms that implement those stipulations given a real set of traffic matrices.

%A generic traffic model is a way of generating the six matrices described in \Section{representations}. A trace-derived traffic model transforms the matrices for an actual trace of network behavior into a simplified or conditional form. For experimental comparison, the dimensions of the matrices should all be preserved. If a trace-derived model produces experimental performance metrics that are similar to those produced by the original trace data, then simplifications made by the model are viable; if the performance is distorted, then the simplifications are discarding essential information about the traffic pattern.

%\subsection{Uniformity}

%% TODO: differentiate between restrictive versions of models and transformative versions.
%% TODO: distinguish uniform, marginal and conditional models.

%\subsection{Marginality}

%Most approaches to traffic modeling that go beyond uniformity assumptions, instead describe marginal properties of various aspects of traffic behavior. For example, {\FHC}~\cite{Hernandez06:spatio-temporal-modeling} provide highly convincing parametric models for six marginal properties of wireless network traffic: session (node) arrivals follow a time-varying Poisson process; per-session flow inter-arrival times are Lognormally distributed; flows per session (node) follow a BiPareto distribution; flow sizes follow a BiPareto distribution. This is certainly much greater detail than simply assuming that all nodes and flows are identical.

%How do marginal models translate into the algebraic language of the general matrix model? Whereas uniformity assumptions for nodes,

%Another benefit of the matrix model is that all aspects of network behavior are determined concurrently. We are not left wondering what to do about source and destination nodes or flow start and end times after we have computed our simplified packet behaviors: the same transformation that average the packet behaviors also naturally averages the start and

@@

The above procedure allows us to sample random values for each property in accordance with the behavioral description implied by $\vec{f}$.
This allows us to stochastically generate a sequence of packets in accordance with a row from an arbitrary \caps{GMM} matrix instance using the following procedure:
\begin{enumerate}
\item Sample random source and destination node pairs.
Since a flow must have distinct source and destination nodes, the sampling of endpoints must be done jointly, avoiding collisions.
The simplest technique is the rejection method:
if the same node is chosen for both source and destination, reject that pair and begin the selection process again.
\item Next, randomly sample the number of bytes.
\item The packet size and inter-packet interval vectors, $\vec{z}$ and $\vec{v}$, allow us to compute the expected average packet size and inter-packet intervals for the flow (see~\Section{flow-totals}), call them $\mean{z}$ and $\mean{v}$.
From these, together with the flow size in bytes, we estimate the expected duration of the flow:
$\mean{d} = \fracx{b\mean{v}}{\mean{z}}$.
\item Randomly sample a start time for the flow. Ensure that the start time plus the expected duration, $\mean{d}$, does not exceed the maximum simulation time for the workflow by using the rejection method.
\item The first packet is sent at the chosen start time.
The size of each packet is determined by sampling a random size value.
The interval until the next packet is determined by sampling a random interval value.
The packet stream ends when the number of bytes allocated to the flow have been emitted or when the packet emission time exceeds $t_{\max}$.
The last packet is only the size of the remaining number of bytes.
\end{enumerate}
Some remarks about the procedure:
\begin{itemize}
\item For some vectors in $\R^{f \cross N}$, it may be impossible to choose distinct source and destination nodes or flow sizes and start times satisfying the procedure.
However, for any vector that is a sum of vectors representing valid flows---\latin{i.e.} ones having distinct source and destination nodes and feasible combinations of start time, duration, and packet behaviors---the procedure will terminate.
\item Because the representation $\phi$ models the seven properties independent of each other, it is impossible to do better than to sample the properties independently, modulo the requirements of the procedure.
In the case of a row which is simple a representation of an actual flow, this makes no difference, except for the generation of packets (which are modeled independently).
In the case of composite rows, however, this implies that flow properties are modeled independent of each other.
\end{itemize}
Despite these remarks, we will show in our experimental evaluation, that this procedure generates sufficiently realistic wireless workloads.

>>>>

\newfootnote{\onesnote}{%
Through out this paper, $\ones$ denotes a matrix of all ones; dimensions of the matrix are inferred by context.
Where necessary, we disambiguate the dimensions by explicitly specifying the dimensions of the final matrix product, as we do here.
}

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The flows vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\trans{\ones} = \mat{V}\trans{\ones} \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones}}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\trans{\ones}} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones}.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vector coordinates, as it does in Matlab.

@@

The total number of source flows for each node is given by the vector $\trans{\mat{S}}\ones \in \R^n$, and the total number of destination flows is given by $\trans{\mat{D}}\ones \in \R^n$.
The number of flows between each pair of nodes in the network is expressed by the matrix product $\trans{\mat{S}}\mat{D}\in\R^{n \times n}$.
That is $(\trans{\mat{S}}\mat{D})_{ij}$ is the number of flows from node $i$ to node $j$.
Interpreting this sparse matrix as a weighted graph immediately yields the source-destination flow communication graph.
\Figure{trace-vs-uniform} gives two visual examples of such graphs.
Similar graphs counting other quantities can readily be computed by inserting the appropriate weighting matrix.
For example, we may compute the inter-node packet transmission graph:
\begin{align}
\trans{\mat{S}}\diag(\vec{\Sigma}_\pkts)\mat{D}\in\R^{n \times n}.
\end{align}
Here $\vec{\Sigma}_\pkts$ is the byte vector defined in \Equation{packet-count}, and the ``$\diag$'' operator gives the square, diagonal matrix with the given vector of values on its diagonal.
Similar graphs for total bytes and total duration of flows may be computed using $\mat{\Sigma}_\bytes$ or $\mat{\Sigma}_\ival$ in place of $\mat{\Sigma}_\pkts$.

@@

Since uniform behaviors entail homogeneity of properties with respect to each flow individually, a trace matrix can be transformed to a matrix satisfying the model's assumptions via right matrix multiplication.
Right multiplication mixes the elements within each row, and if the mixing weights are uniform, the result is uniform behavior.
For example, to make the roles of the nodes with respect to each flow statistically identical, we transform $\mat{S}$ and $\mat{D}$:
\begin{align}
\mat{S}' &= \rStoch(\mat{S}\ones) = \smallfrac{1}{n} \mat{S}\ones \in \R^{f \times n} \\
\mat{D}' &= \rStoch(\mat{D}\ones) = \smallfrac{1}{n} \mat{D}\ones\in \R^{f \times n}.
\end{align}
The ``$\rStoch$'' operator scales each row to sum to unity, thus making the entire matrix row-stochastic;
in this case, this is equivalent to scaling by $\smallfrac{1}{n}$.
These transformations of $\mat{S}$ and $\mat{D}$ make all the values in each flow's row identically the average of the original $n$ values.
As another example, the constant bit-rate (\caps{CBR}) flow model, in its strictest sense, is an intra-flow model, which stipulates that all the packets in each flow behave identically, having identical sizes and intervals;
thus each flow's bit-rate is constant, as the name implies.
The strict \caps{CBR} model can be easily expressed with the packets-bytes-duration (\caps{PBD}) model used as an example in \Section{representations}.
The pair of matrices $[\mat{Z}~\mat{V}]$ is transformed to \caps{PBD} form using the vectors defined in \Section{flow-totals}:
$[\mat{Z}~\mat{V}]\,\mat{\Gamma}\in\R^{f \times 3}$, where
\begin{align}
\mat{\Gamma}=\begin{pmatrix}
\ones & \vec{\sigma} & \zeros \\
\zeros & \zeros & \vec{\tau}
\end{pmatrix} \in \R^{(d_v+d_z)\times{3}}.
\end{align}
\Figure{trace-vs-uniform} graphically depicts examples of uniform behaviors as compared to realistic behaviors from traces.

@@

Marginality is an orthogonal concept to uniformity:
the distribution of some property is identical \textit{across} all flows.
For example, if we determine a distribution of flow sizes across the entire network and assume that this distribution applies independent of other flow properties, this is a marginal model for flow size.
Marginal behavior is effected by left multiplication by a matrix with uniform columns.
This specific example is generated by left-uniformizing the flow size matrix:
$\mat{B}' = \smallfrac{1}{f}\ones\mat{B}$.
The traffic models proposed by {\FHC} are all marginal:
they propose certain network-wide parametric distributions for start times, flow sizes and the number of flows per node.
These models do not account for non-independence between these and other flow properties.
We will discuss this limitation and its implications when we analyze our experimental results.

@@

The final form of homogenization we consider, is conditionality.
This is a restricted form of marginality:
we may assume that marginal distributions apply to all the flows in certain groupings.
For example, we can provide a distribution of flow sizes on a per-source basis.
That is, each source node can have its \textit{own} distribution, and the sizes of its flows are drawn from that distribution, independent of their other properties.
This is simply accomplished by left-multiplication by a non-uniform matrix.
For example, to make flow behavior uniform per source, consider the ``source-conditioning'' matrix:
$\trans{\mat{S}}\mat{S} \in \R^{n \times n}$.
This matrix has $(\trans{\mat{S}}\mat{S})_{ij} = 1$ if and only if flows $i$ and $j$ have the same source node.
To condition flow behavior by source, we left-multiply by the stochasticized source-condtioning matrix:
\begin{align}
  \mat{F}'= \rStoch(\trans{\mat{S}}\mat{S})\mat{F}.
\end{align}
In this case, rows do not have the same sums, so the ``$\rStoch$'' operator is not equivalent to scalar multiplication.
Per destination uniformity can be achieved similarly, replacing $\mat{S}$ with $\mat{D}$.

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the aggregate behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.

@@

The above procedure allows us to sample random values for each property in accordance with the behavioral description implied by $\vec{f}$.
This allows us to stochastically generate a sequence of packets in accordance with a row from an arbitrary \caps{GMM} matrix instance using the following procedure:
\begin{enumerate}
\item Sample random source and destination node pairs.
Since a flow must have distinct source and destination nodes, the sampling of endpoints must be done jointly, avoiding collisions.
The simplest technique is the rejection method:
if the same node is chosen for both source and destination, reject that pair and begin the selection process again.
\item Next, randomly sample the number of bytes.
\item The packet size and inter-packet interval vectors, $\vec{z}$ and $\vec{v}$, allow us to compute the expected average packet size and inter-packet intervals for the flow (see~\Section{flow-totals}), call them $\mean{z}$ and $\mean{v}$.
From these, together with the flow size in bytes, we estimate the expected duration of the flow:
$\mean{d} = \fracx{b\mean{v}}{\mean{z}}$.
\item Randomly sample a start time for the flow. Ensure that the start time plus the expected duration, $\mean{d}$, does not exceed the maximum simulation time for the workflow by using the rejection method.
\item The first packet is sent at the chosen start time.
The size of each packet is determined by sampling a random size value.
The interval until the next packet is determined by sampling a random interval value.
The packet stream ends when the number of bytes allocated to the flow have been emitted or when the packet emission time exceeds $t_{\max}$.
The last packet is only the size of the remaining number of bytes.
\end{enumerate}
Some remarks about the procedure:
\begin{itemize}
\item For some vectors in $\R^{f \cross N}$, it may be impossible to choose distinct source and destination nodes or flow sizes and start times satisfying the procedure.
However, for any vector that is a sum of vectors representing valid flows---\latin{i.e.} ones having distinct source and destination nodes and feasible combinations of start time, duration, and packet behaviors---the procedure will terminate.
\item Because the representation $\phi$ models the seven properties independent of each other, it is impossible to do better than to sample the properties independently, modulo the requirements of the procedure.
In the case of a row which is simple a representation of an actual flow, this makes no difference, except for the generation of packets (which are modeled independently).
In the case of composite rows, however, this implies that flow properties are modeled independent of each other.
\end{itemize}
Despite these remarks, we will show in our experimental evaluation, that this procedure generates \emph{sufficiently realistic} wireless workloads~\cite{Karpinski07:realism,Karpinski07:cbr-failure}.

### 2008-06-13 tables/traffic_models.tex
Lots of work on Common Assumptions section.

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} &
--- &
the general matrix model
\\\hline\hline
time uniform &
$\mat{A}'=\mat{A}(\ones{d_t \times d_t}/d_t)$ &
all start times are equally likely
\\\hline
node uniform &
$\mat{S}'=\mat{S}(\ones{n \times n}/n)$~~~~$\mat{D}'=\mat{D}(\ones{n \times n}/n)$ &
nodes behave stochastically identically with respect to flows
\\\hline
full uniform &
\textit{all uniform transformations} &
applies all the uniformity assumptions of the above models
\\\hline\hline
time marginal &
$\mat{A}'=(\ones{f \times f}/f)\mat{A}$ &
start times chosen from marginal distribution of start times
\\\hline
size marginal &
$\mat{B}'=(\ones{f \times f}/f)\mat{B}$ &
flow size (bytes) is chosen independently of other properties
\\\hline
node marginal &
$\mat{S}'=(\ones{f \times f}/f)\mat{S}$~~~~$\mat{D}'=(\ones{f \times f}/f)\mat{D}$ &
nodes behave distinctly, but behavior is independent of flows
\\\hline
packet marginal &
$\mat{Z}'=(\ones{f \times f}/f)\mat{Z}$~~~~$\mat{V}'=(\ones{f \times f}/f)\mat{V}$ &
packet behavior is variable bit-rate, aggregated across all flows
\\\hline
full marginal &
\textit{all marginal transformations} &
applies all the marginality assumptions of the above four models
\\\hline\hline
source conditional &
$\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$ &
flow behaviors are aggregated on a per source-node basis
\\\hline
dest conditional &
$\mat{F}'=(\trans{\mat{DD}}/f)\mat{F}$ &
flow behaviors are aggregated on a per destination-node basis
\\\hline
mixed conditional &
$\mat{F}'=\frac{1}{2f}(\trans{\mat{SS}}+\trans{\mat{DD}})\mat{F}$ &
flow behaviors are aggregated on a mixed source/destination basis
\\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} &
--- &
the general matrix model
\\\hline\hline
time uniform &
$\mat{A}'=\mat{A}(\ones/d_t)$ &
all start times are equally likely
\\\hline
node uniform &
$\mat{S}'=\mat{S}(\ones/n)$~~~~$\mat{D}'=\mat{D}(\ones/n)$ &
nodes behave stochastically identically with respect to flows
\\\hline
full uniform &
\textit{all uniform transformations} &
applies all the uniformity assumptions of the above models
\\\hline\hline
time marginal &
$\mat{A}'=(\ones/f)\mat{A}$ &
start times chosen from marginal distribution of start times
\\\hline
size marginal &
$\mat{B}'=(\ones/f)\mat{B}$ &
flow size (bytes) is chosen independently of other properties
\\\hline
node marginal &
$\mat{S}'=(\ones/f)\mat{S}$~~~~$\mat{D}'=(\ones/f)\mat{D}$ &
nodes behave distinctly, but behavior is independent of flows
\\\hline
packet marginal &
$\mat{Z}'=(\ones/f)\mat{Z}$~~~~$\mat{V}'=(\ones/f)\mat{V}$ &
packet behavior is variable bit-rate, aggregated across all flows
\\\hline
full marginal &
\textit{all marginal transformations} &
applies all the marginality assumptions of the above four models
\\\hline\hline
source conditional &
$\mat{F}'=(\trans{\mat{SS}}/f)\mat{F}$ &
flow behaviors are aggregated on a per source-node basis
\\\hline
dest conditional &
$\mat{F}'=(\trans{\mat{DD}}/f)\mat{F}$ &
flow behaviors are aggregated on a per destination-node basis
\\\hline
mixed conditional &
$\mat{F}'=\frac{1}{2f}(\trans{\mat{SS}}+\trans{\mat{DD}})\mat{F}$ &
flow behaviors are aggregated on a mixed source/destination basis
\\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-2em}
\end{table*}
